---
title: "Primary Analyses"
output:
  html_document:
    df_print: paged
  pdf_document: default
---


```{r, include = FALSE, echo = FALSE}
dat_all <- read_csv(here("data", "merged_data_final.csv"))

dat_m <- dat_all %>% filter(Sex == "M")
dat_f <- dat_all %>% filter(Sex == "F")
```


# Descriptive statistics overall and by study 
```{r, echo = FALSE}
(overall <- dat_all %>%
  summarize(
    mean_age = mean(age),
    sd_age = sd(age),
    min_age = min(age),
    max_age = max(age),
    total_n = n()
  ))

(study <- dat_all %>%
  group_by(Study) %>%
  summarize(
    mean_age = mean(age),
    sd_age = sd(age),
    min_age = min(age),
    max_age = max(age),
    total_n = n()
  ))

```






#########################################################################################################################
# Overall piecewise regression
#########################################################################################################################

## Create function to run piecewise analyses and gather relevant output in single dataframe
```{r}
run_segmented_analysis <- function(data, outcome_var, alternative = "two.sided", npsi = 1, seed = 100) {
  stopifnot(outcome_var %in% names(data))

  # Set seed for reproducibility
  set.seed(seed)

  # Formula
  formula <- as.formula(paste(outcome_var, "~ age"))

  # Fit linear and segmented models
  fit_lm <- lm(formula, data = data)
  fit_seg <- segmented::segmented(fit_lm, seg.Z = ~ age, npsi = npsi)

  # Extract breakpoint estimate and CI
  bp_est <- segmented::summary.segmented(fit_seg)$psi["psi1.age", "Est."]
  bp_ci <- confint.segmented(fit_seg)["psi1.age", c("CI(95%).low", "CI(95%).up")]

  # Slope estimates before and after breakpoint
  slopes <- segmented::slope(fit_seg)$age

  # Davies test for slope difference
  pscore <- segmented::pscore.test(fit_seg, seg.Z = ~ age, k = 10, alternative = alternative)$p.value

  # Tidy output
  tibble::tibble(
    outcome = outcome_var,
    breakpoint = round(bp_est, 2),
    ci_lower = round(bp_ci[1], 2),
    ci_upper = round(bp_ci[2], 2),
    slope_before = round(slopes[1], 4),
    slope_after = round(slopes[2], 4),
    slope_diff = round(slopes[2] - slopes[1], 4),
    pscore_pval = signif(pscore, 3),
    model = list(fit_seg)
  )
}

```

## Age vs PReFx
```{r}
(prefx_fit <- run_segmented_analysis(data = dat_all, outcome = "prefx_std", alternative = "less"))
```


## Age vs WM Hypointensity
```{r}
(wmh_fit <- run_segmented_analysis(data = dat_all, outcome = "log_hypo", alternative = "greater"))
```

## Age vs Fluid Ability
```{r}
(fluid_fit <- run_segmented_analysis(data = dat_all, outcome = "fluid_std", alternative = "less"))
```

## Age vs Verbal Ability
```{r}
(verbal_fit <- run_segmented_analysis(data = dat_all, outcome = "verbal_std", alternative = "less"))
```

### Multiple comparisons correction of p-values for piecewise estimates via Holm-Bonferroni (4) 
```{r, echo = FALSE}

options(scipen = 100, digits = 4) # stop use of scientific notation 
p_vec_seg <- c(prefx_fit$pscore_pval, wmh_fit$pscore_pval, fluid_fit$pscore_pval, verbal_fit$pscore_pval)

p_holm_seg <- p.adjust(p = p_vec_seg, method = "holm")

p_holm_seg
```


# Piecewise regression plots
## Define a function for reproducing breakpoint plots
```{r}
make_breakpoint_plot <- function(data,
                                 age_var,
                                 y_var,
                                 fit_object,
                                 breakpoint_coords = NULL,
                                 secondary_breaks = NULL,
                                 plot_tag = NULL,
                                 title = NULL,
                                 subtitle = NULL,
                                 y_label = NULL,
                                 ribbon_color = "black",
                                 line_color = "blue") {
  # Extract fitted values and confidence intervals from segmented model
  fit_vals <- broken.line(fit_object)$fit
  se_vals  <- broken.line(fit_object, se.fit = TRUE)$se.fit
  ribbon_low  <- fit_vals - 1.96 * se_vals
  ribbon_high <- fit_vals + 1.96 * se_vals

  # Auto-calculate breakpoint_coords if not provided
  if (is.null(breakpoint_coords)) {
    bp_x <- tryCatch(segmented::summary.segmented(fit_object)$psi["psi1.age", "Est."], error = function(e) NA)
    bp_y <- tryCatch(predict(fit_object, newdata = data.frame(age = bp_x)), error = function(e) NA)
    if (!is.na(bp_x) && !is.na(bp_y)) {
      breakpoint_coords <- c(bp_x, bp_y)
    }
  }

  # Try to auto-extract CI bounds if not supplied
  if (is.null(secondary_breaks)) {
    secondary_breaks <- tryCatch(confint.segmented(fit_object)["psi1.age", c("CI(95%).low", "CI(95%).up")], error = function(e) NULL)
  }

  # Begin ggplot
  p <- ggplot(data, aes_string(x = age_var, y = y_var)) +

    # Add dot at estimated breakpoint
    {
      if (!is.null(breakpoint_coords)) {
        geom_point(data = NULL,
                   aes(x = breakpoint_coords[1], y = breakpoint_coords[2]),
                   shape = 19, colour = "black", size = 4)
      }
    } +

    # Add fitted line
    geom_line(aes_string(x = age_var, y = "fit_vals"),
              linewidth = 2, colour = line_color, alpha = 0.65) +

    # Add confidence ribbon
    geom_ribbon(aes_string(
      x = age_var,
      y = "fit_vals",
      ymin = "ribbon_low",
      ymax = "ribbon_high"
    ),
    fill = ribbon_color, alpha = 0.15) +

    # Raw data points colored by sex
    geom_point(aes(color = Sex), size = 2, alpha = 0.65) +

    # Add vertical lines at CI bounds
    {
      if (!is.null(secondary_breaks)) {
        geom_vline(data = data.frame(x = secondary_breaks),
                   aes(xintercept = x),
                   linetype = "dotted", colour = "black", size = 1, alpha = 0.5)
      }
    } +

    # Labels
    labs(
      tag = plot_tag,
      title = title,
      subtitle = subtitle,
      x = "Age (years)",
      y = y_label
    ) +

    # Theme
    theme(
      axis.title     = element_text(size = 14),
      plot.title     = element_text(face = "bold", size = 16),
      plot.subtitle  = element_text(size = 14)
    )

  return(p)
}


```


```{r, echo=FALSE, message = FALSE, warning=FALSE}

(age_prefx <- make_breakpoint_plot(data = dat_all,
                                  age_var = "age",
                                  y_var = "prefx_std",
                                  fit_object = prefx_fit$model[[1]],
                                  breakpoint_coords = NULL,
                                  secondary_breaks = NULL,
                                  title = "Age vs Cerebral Arterial Health",
                                  subtitle = "'Best' breakpoint estimate ≈ 53 years",
                                  y_label = "PReFx (z-score)"))

ggsave(here("figures", "age_prefx_piecewise.png"), age_prefx, width = 6.5, height = 4, units= "in", dpi = 300)
```

```{r, echo=FALSE, message = FALSE, warning=FALSE}
dat_wmh <- dat_all %>% dplyr::select(age,log_hypo, Sex) %>% drop_na()

(age_wmh <- make_breakpoint_plot(data = dat_wmh,
                                  age_var = "age",
                                  y_var = "log_hypo",
                                  fit_object = wmh_fit$model[[1]],
                                  breakpoint_coords = NULL,
                                  secondary_breaks = NULL,
                                  title = "Age vs White Matter Lesion Volume",
                                  subtitle = "'Best' breakpoint estimate ≈ 61 years",
                                  y_label = "log(WMSA Volume in mm³)"))

ggsave(here("figures", "age_wmh_piecewise.png"), age_wmh, width = 6.5, height = 4, units= "in", dpi = 300)
```

```{r, echo=FALSE, message= FALSE, warning=FALSE}
dat_fluid <- dat_all %>% dplyr::select(age, fluid_std, Sex) %>% mutate(Sex = Sex) %>% drop_na()

(age_fluid <- make_breakpoint_plot(data = dat_fluid,
                                  age_var = "age",
                                  y_var = "fluid_std",
                                  fit_object = fluid_fit$model[[1]],
                                  breakpoint_coords = NULL,
                                  secondary_breaks = NULL,
                                  title = "Age vs Fluid Cognition",
                                  subtitle = "'Best' breakpoint estimate ≈ 55 years",
                                  y_label = "Fluid Cognitive Ability (z-score)"))


ggsave(here("figures", "age_fluid_piecewise.png"), age_fluid, width = 6.5, height = 4, units= "in", dpi = 300)
```

```{r echo=FALSE, warning=FALSE}
dat_verbal <- dat_all %>% dplyr::select(age, verbal_std, Sex) %>% mutate(Sex = Sex) %>% drop_na()

(age_verbal <- make_breakpoint_plot(data = dat_verbal,
                                  age_var = "age",
                                  y_var = "verbal_std",
                                  fit_object = verbal_fit$model[[1]],
                                  breakpoint_coords = NULL,
                                  secondary_breaks = NULL,
                                  title = "Age vs Crystallized Cognition",
                                  subtitle = "'Best' breakpoint estimate ≈ 67 years",
                                  y_label = "Crystallized Cognitive Ability (z-score)"))


ggsave(here("figures", "age_verbal_piecewise.png"), age_verbal, width = 6.5, height = 4, units= "in", dpi = 300)
```



#########################################################################################################################
# Piecewise regression by sex 
#########################################################################################################################

## Male PReFx
```{r}
(prefx_male <- run_segmented_analysis(data = dat_m, outcome = "prefx_std", alternative = "less"))
```
## Female PReFx
```{r}
(prefx_female <- run_segmented_analysis(data = dat_f, outcome = "prefx_std", alternative = "less"))
```


## Male WMH
```{r}
(wmh_male <- run_segmented_analysis(data = dat_m, outcome = "log_hypo", alternative = "greater"))
```
## Female WMH
```{r}
(wmh_female <- run_segmented_analysis(data = dat_f, outcome = "log_hypo", alternative = "greater"))
```

## Male Fluid Ability
```{r}
(fluid_male <- run_segmented_analysis(data = dat_m, outcome = "fluid_std", alternative = "less"))
```
## Female Fluid Ability
```{r}
(fluid_female <- run_segmented_analysis(data = dat_f, outcome = "fluid_std", alternative = "less"))
```

## Male Verbal Ability
```{r}
(verbal_male <- run_segmented_analysis(data = dat_m, outcome = "verbal_std", alternative = "less"))
```
## Female Verbal Ability
```{r}
(verbal_female <- run_segmented_analysis(data = dat_f, outcome = "verbal_std", alternative = "less"))
```


### Multiple comparisons correction of all sex piecewise estimates (8) 
```{r, echo = FALSE}
options(scipen = 999) # stop use of scientific notation
p.vec.seg <- c(prefx_male$pscore_pval,
               prefx_female$pscore_pval,
               wmh_male$pscore_pval,
               wmh_female$pscore_pval,
               fluid_male$pscore_pval,
               fluid_female$pscore_pval,
               verbal_male$pscore_pval,
               verbal_female$pscore_pval)

p.holm.seg <- p.adjust(p = p.vec.seg, method = "holm")

p.holm.seg
```


#########################################################################################################################
# Piecewise plots by sex 
#########################################################################################################################

## Create wrapper function to reproduce piecewise sex plots
```{r}
make_dual_breakpoint_plot <- function(data_m,
                                      data_f,
                                      age_var,
                                      y_var,
                                      fit_m,
                                      fit_f,
                                      break_m = NULL,        # coordinate: c(x, y)
                                      break_f = NULL,        # coordinate: c(x, y)
                                      break_ci_m = NULL,
                                      break_ci_f = NULL,
                                      plot_tag = NULL,
                                      title = NULL,
                                      subtitle = NULL,
                                      y_label = NULL,
                                      point_size = 2,
                                      ribbon_alpha = 0.15,
                                      line_alpha = 0.65,
                                      colors = c(male = "blue", female = "red")) {

  # Fit predictions
  fit_vals_m     <- broken.line(fit_m)$fit
  se_vals_m      <- broken.line(fit_m, se.fit = TRUE)$se.fit
  ribbon_low_m   <- fit_vals_m - 1.96 * se_vals_m
  ribbon_high_m  <- fit_vals_m + 1.96 * se_vals_m

  fit_vals_f     <- broken.line(fit_f)$fit
  se_vals_f      <- broken.line(fit_f, se.fit = TRUE)$se.fit
  ribbon_low_f   <- fit_vals_f - 1.96 * se_vals_f
  ribbon_high_f  <- fit_vals_f + 1.96 * se_vals_f

  # Get p-values for slope difference
  pval_m <- tryCatch(pscore.test(fit_m, seg.Z = ~age, k = 10)$p.value, error = function(e) NA)
  pval_f <- tryCatch(pscore.test(fit_f, seg.Z = ~age, k = 10)$p.value, error = function(e) NA)

  sig_m <- !is.na(pval_m) && pval_m < 0.05
  sig_f <- !is.na(pval_f) && pval_f < 0.05

  # Auto breakpoints
  if (is.null(break_m) && sig_m) {
    bp_x_m <- tryCatch(summary(fit_m)$psi["psi1.age", "Est."], error = function(e) NA)
    bp_y_m <- tryCatch(predict(fit_m, newdata = data.frame(age = bp_x_m)), error = function(e) NA)
    if (!is.na(bp_x_m) && !is.na(bp_y_m)) break_m <- c(bp_x_m, bp_y_m)
  }

  if (is.null(break_f) && sig_f) {
    bp_x_f <- tryCatch(summary(fit_f)$psi["psi1.age", "Est."], error = function(e) NA)
    bp_y_f <- tryCatch(predict(fit_f, newdata = data.frame(age = bp_x_f)), error = function(e) NA)
    if (!is.na(bp_x_f) && !is.na(bp_y_f)) break_f <- c(bp_x_f, bp_y_f)
  }

  # Auto CI bounds
  if (is.null(break_ci_m) && sig_m) {
    break_ci_m <- tryCatch(confint.segmented(fit_m)["psi1.age", c("CI(95%).low", "CI(95%).up")], error = function(e) NULL)
  }

  if (is.null(break_ci_f) && sig_f) {
    break_ci_f <- tryCatch(confint.segmented(fit_f)["psi1.age", c("CI(95%).low", "CI(95%).up")], error = function(e) NULL)
  }

  # Begin plot
  p <- ggplot() +

    # Male breakpoint dot
    {
      if (sig_m && !is.null(break_m)) {
        geom_point(data = NULL,
                   aes(x = break_m[1], y = break_m[2]),
                   shape = 21, size = 5, fill = "black", color = "black")
      }
    } +

    # Female breakpoint dot
    {
      if (sig_f && !is.null(break_f)) {
        geom_point(data = NULL,
                   aes(x = break_f[1], y = break_f[2]),
                   shape = 21, size = 5, fill = "black", color = "black")
      }
    } +

    # Raw points
    geom_point(data = data_m, aes_string(x = age_var, y = y_var),
               colour = colors["male"], size = point_size, alpha = 0.5) +
    geom_point(data = data_f, aes_string(x = age_var, y = y_var),
               colour = colors["female"], size = point_size, alpha = 0.5) +

    # Fitted lines
    geom_line(data = data_m, aes_string(x = age_var, y = "fit_vals_m"),
              linewidth = 2, colour = colors["male"], alpha = line_alpha) +
    geom_line(data = data_f, aes_string(x = age_var, y = "fit_vals_f"),
              linewidth = 2, colour = colors["female"], alpha = line_alpha) +

    # Confidence ribbons
    geom_ribbon(data = data_m,
                aes_string(x = age_var, y = "fit_vals_m",
                           ymin = "ribbon_low_m", ymax = "ribbon_high_m"),
                fill = colors["male"], alpha = ribbon_alpha) +
    geom_ribbon(data = data_f,
                aes_string(x = age_var, y = "fit_vals_f",
                           ymin = "ribbon_low_f", ymax = "ribbon_high_f"),
                fill = colors["female"], alpha = ribbon_alpha) +

    # CI lines for males
    {
      if (sig_m && !is.null(break_ci_m)) {
        geom_vline(data = data.frame(x = break_ci_m),
                   aes(xintercept = x),
                   linetype = "dotted", color = colors["male"],
                   size = 1, alpha = 0.5)
      }
    } +

    # CI lines for females
    {
      if (sig_f && !is.null(break_ci_f)) {
        geom_vline(data = data.frame(x = break_ci_f),
                   aes(xintercept = x),
                   linetype = "dotted", color = colors["female"],
                   size = 1, alpha = 0.5)
      }
    } +

    labs(
      tag = plot_tag,
      title = title,
      subtitle = subtitle,
      x = "Age (years)",
      y = y_label
    ) +

    theme(
      plot.title    = element_markdown(lineheight = 1.1, size = 16),
      legend.text   = element_markdown(size = 11),
      plot.caption  = element_markdown(size = 9, hjust = 0.5),
      axis.title    = element_text(size = 12)
    )

  return(p)
}

```



```{r, echo = FALSE, message = FALSE}
dat_m <- dat_all %>% filter(Sex == "M") %>%  dplyr::select(age, prefx_std, Sex) %>% drop_na()
dat_f <- dat_all %>%  filter(Sex == "F")%>% dplyr::select(age, prefx_std, Sex) %>% drop_na()

(sex_prefx <- make_dual_breakpoint_plot(data_m = dat_m,
                                       data_f = dat_f,
                                       age_var = "age",
                                       y_var = "prefx_std",
                                       fit_m = prefx_male$model[[1]],
                                       fit_f = prefx_female$model[[1]],
                                       break_m = NULL,        # coordinate: c(x, y)
                                       break_f = NULL,        # coordinate: c(x, y)
                                       break_ci_m = NULL,
                                       break_ci_f = NULL,
                                       plot_tag = NULL,
                                       title = "**Age vs Pulse Relaxation Function (PReFx)**  
    <span style='color:red; font-size:11pt'>**Females = Red**</span>,
    <span style='color:blue; font-size:11pt'>**Males = Blue**</span>",
                                       subtitle = NULL,
                                       y_label = "PReFx (z-score)"))


ggsave(here("figures", "age_prefx_sex.png"), sex_prefx, width = 6.5, height = 4, units= "in", dpi = 300)
```


```{r, echo = FALSE, message = FALSE}
dat_m <- dat_all %>% filter(Sex == "M") %>%  dplyr::select(age, log_hypo, Sex) %>% drop_na()
dat_f <- dat_all %>%  filter(Sex == "F")%>% dplyr::select(age, log_hypo, Sex) %>% drop_na()

(sex_wmh <- make_dual_breakpoint_plot(data_m = dat_m,
                                       data_f = dat_f,
                                       age_var = "age",
                                       y_var = "log_hypo",
                                       fit_m = wmh_male$model[[1]],
                                       fit_f = wmh_female$model[[1]],
                                       break_m = NULL,        # coordinate: c(x, y)
                                       break_f = NULL,        # coordinate: c(x, y)
                                       break_ci_m = NULL,
                                       break_ci_f = NULL,
                                       plot_tag = NULL,
                                       title = "**Age vs White Matter Lesion Volume**  
    <span style='color:red; font-size:11pt'>**Females = Red**</span>,
    <span style='color:blue; font-size:11pt'>**Males = Blue**</span>",
                                       subtitle = NULL,
                                       y_label = "log(WMSA Volume in mm³)"))


ggsave(here("figures", "age_wmh_sex.png"), sex_wmh, width = 6.5, height = 4, units= "in", dpi = 300)
```


```{r, echo = FALSE, message = FALSE}
dat_m <- dat_all %>% filter(Sex == "M") %>%  dplyr::select(age, fluid_std, Sex) %>% drop_na()
dat_f <- dat_all %>%  filter(Sex == "F")%>% dplyr::select(age, fluid_std, Sex) %>% drop_na()

(sex_fluid <- make_dual_breakpoint_plot(data_m = dat_m,
                                       data_f = dat_f,
                                       age_var = "age",
                                       y_var = "fluid_std",
                                       fit_m = fluid_male$model[[1]],
                                       fit_f = fluid_female$model[[1]],
                                       title = "**Age vs Fluid Cognitive Ability**  
    <span style='color:red; font-size:11pt'>**Females = Red**</span>,
    <span style='color:blue; font-size:11pt'>**Males = Blue**</span>",
                                       subtitle = NULL,
                                       y_label = "Fluid Cognition Composite (z-score)"))

ggsave(here("figures", "age_fluid_sex.png"), sex_fluid, width = 6.5, height = 4, units= "in", dpi = 300)
```

```{r, echo = FALSE, message = FALSE}
dat_m <- dat_all %>% filter(Sex == "M") %>%  dplyr::select(age, verbal_std, Sex) %>% drop_na()
dat_f <- dat_all %>%  filter(Sex == "F")%>% dplyr::select(age, verbal_std, Sex) %>% drop_na()

(sex_verbal <- make_dual_breakpoint_plot(data_m = dat_m,
                                       data_f = dat_f,
                                       age_var = "age",
                                       y_var = "verbal_std",
                                       fit_m = verbal_male$model[[1]],
                                       fit_f = verbal_female$model[[1]],
                                       title = "**Age vs Crystallized Cognitive Ability**  
    <span style='color:red; font-size:11pt'>**Females = Red**</span>,
    <span style='color:blue; font-size:11pt'>**Males = Blue**</span>",
                                       subtitle = NULL,
                                       y_label = "Crystallized Cognition Composite (z-score)"))

ggsave(here("figures", "age_verbal_sex.png"), sex_verbal, width = 6.5, height = 4, units= "in", dpi = 300)
```


# Two mediator sequential mediation

**Define a reusable function to specify SEM models and fit them using lavaan::sem()**
```{r}
serial_med <- function(x, m1, m2, y, cov, dat, boot = 5000, seeder = 100) {
  
  set.seed(seeder)
  
  # Ensure the model string is properly formatted using str_glue
  med.model <- str_glue("
    # Regressions
    {m1} ~ a1*{x} + cov1*{cov}  # Label the a coefficient in the M1 regression.
    {m2} ~ a2*{x} + d21*{m1} + cov2*{cov}  # Label the a coefficientS in the M2 regression.
    {y} ~ cPrime*{x} + b1*{m1} + b2*{m2} + cov3*{cov}

    # Define New Parameters (products of coefficients)
    ab1 := a1 * b1
    ab2 := a2 * b2
    ab3 := a1 * d21 * b2
    c := cPrime + ab1 + ab2 + ab3
  ", .sep = "")

 # Fit the model using lavaan's sem function
  fit <- lavaan::sem(model = med.model, data = dat, test = "bootstrap", bootstrap = boot)

  # Extract parameter estimates, including bootstrapping if needed
  param_est <- parameterEstimates(fit, standardized = TRUE, level = 0.95, boot.ci.type = "bca.simple")
  
  #  Tidy output
  tibble::tibble(
    parameter = c("a1*b1", "a2*b2", "a1*d21*b2"),
    coef_std = c(param_est[param_est$label == "ab1", "std.all"],
                 param_est[param_est$label == "ab2", "std.all"],
                 param_est[param_est$label == "ab3", "std.all"]),
    ci_lower = c(param_est[param_est$label == "ab1", "ci.lower"],
                 param_est[param_est$label == "ab2", "ci.lower"],
                 param_est[param_est$label == "ab3", "ci.lower"]),
    ci_upper = c(param_est[param_est$label == "ab1", "ci.upper"],
                 param_est[param_est$label == "ab2", "ci.upper"],
                 param_est[param_est$label == "ab3", "ci.upper"]),
    p_value_uncorrected = c(param_est[param_est$label == "ab1", "pvalue"],
                 param_est[param_est$label == "ab2", "pvalue"],
                 param_est[param_est$label == "ab3", "pvalue"])
  )
}
```


## Run mediation analyses and return results for indirect effects

**This takes awhile to run. Consider lowering number of boostrap samples**

**Age -> PReFx -> WMSA -> Fluid Cognition (sex controlled)**
```{r}
(prefx_fluid <- serial_med(x = "age", m1 = "prefx_std", m2 =  "log_hypo", y = "fluid_std", cov = "Sex", dat = dat_all, boot = 5000))
```

**Age -> PReFx -> WMSA -> Verbal Cognition (sex controlled)**
```{r}
(prefx_verbal <- serial_med(x = "age", m1 = "prefx_std", m2 =  "log_hypo", y = "verbal_std", cov = "Sex", dat = dat_all, boot = 5000))

```

### Correct p-values for two-mediator serial indirect effect via Holm-Bonferroni method 
```{r, echo = FALSE}

# options(scipen = 999) # stop use of scientific notation
p.vec.prefx <- c(prefx_fluid$p_value_uncorrected[3], prefx_verbal$p_value_uncorrected[3])
p.holm.prefx <- p.adjust(p = p.vec.prefx, method = "holm")

p.holm.prefx
```

# Medication effects

**Is there an effect of BP or cholesterol medication status on our outcomes of interest when controlling for age? (Only older adults included to satisfy linearity assumption)**

```{r, echo = FALSE}
dat.old <- dplyr::filter(dat_all, age >= 50)

## Beta blocker status
summary(lm(pulse_pressure_clean~beta_blocker*age,data = dat.old))
summary(lm(prefx_std~beta_blocker*age,data = dat.old))
summary(lm(log_hypo~beta_blocker*age,data = dat.old))

## Statins status
summary(lm(pulse_pressure_clean~statins*age,data = dat.old))
summary(lm(prefx_std~statins*age,data = dat.old))
summary(lm(log_hypo~statins*age,data = dat.old))

```